---
title: "Hooper_ESM211_HW2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


### Load packages 

library(tidyverse)
```

<br>

#### 1. Graph of *dN/dt* vs. *N*. 

```{r Question 1}

### Set parameters: 

r = 0.05 # intrinsic growth rate
K = 2000 # carrying capacity 
P = 4 # number of predators (hunters)
a = 0.05 # per-prey attack rate
h = 0.2 # handling time 

f <- function(N) r*N*(1-N/K) - P*((a*N)/(1+a*h*N)) # Here is where you define the function

ggplot(data.frame(N = 0:2025), aes(x = N)) +
  stat_function(fun = f, color = "purple") +
  geom_hline(yintercept = 0) +
  ylab("dN/dt") +
  theme_classic()

```

#### 2. Equilibria 
Based on this graph, there are three equilibria points. One at *N* = 0 (stable), *N* = ~ 490 (unstable), and *N* = 1500 (stable). 



<br>



#### 3. Equilibria at *N* = 0 
- Is there an equilibria at N = 0 for all plausible parameter values?
- For what values of hunter number (P), expressed in terms of the other paramters of the model, is the zero equilibrium locally stable? 
- If your goal is to eliminate the invasive species, what does this tell you about how many hunters you need? 


```{r Question 3}


### Set parameters: 

# f(N) = per-hunter harvest rate

r = 0.05 # intrinsic growth rate
K = 2000 # carrying capacity 
P = 2 # number of predators (hunters)
a = 0.05 # per-prey attack rate
h = 0.2 # handling time 

f <- function(N) r*N*(1-N/K) - P*((a*N)/(1+a*h*N)) # Here is where you define the function

ggplot(data.frame(N = 0:1025), aes(x = N)) +
  stat_function(fun = f, color = "purple") +
  geom_hline(yintercept = 0) +
  ylab("dN/dt") +
  theme_classic()




```
a. Yes, there is an equilibrium at *N* = 0 for all plausible paramter values. Because our harvest rate is zero at *N* = 0, it is an equilibrium point. 
b. When *P* > 1, the zero equilibrium point will be locally stable. 
c. 


<br>


#### 4. Non-zero equilibria equation



<br.



#### 5. Intrinsic Growth Rate and Hunting Rate


<br>



#### 6. Equilibria with different *P* vaues


<br>



#### 7. Bistability


<br>



#### 8. Changing number of hunters

<br.

